Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 DRAFT_lncRNA.Rmd
meeth - hpc comments

```{r,message = FALSE,echo = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", hyperlink = "to.html")
```

@@

>>>>

```{r,message = FALSE,echo = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               eval = FALSE,         # Evaluate code chunks
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", hyperlink = "to.html")
```

@@

## Notes on running code. This workflow is written such that a user an fully reproduce the code. Th
